Numerical and analytical solution of nonlinear electro-kinetic phenomena

### 2012-09-08 notes/work/ch01.tex
LaTeX

Recently, it has been conceived that such type of dynamics
can be very useful in transporting and manipulating micro-
and nanoscale objects for many nanotechnology applications,
such as the self-assembly of superstructures, roving sensors, 
drug-delivery systems and useful nanomachinery 
\cite{howse2007self,paxton2004catalytic,pumera2010electrochemically}.
However, since the analytic model for these electrokinetic
phenomena has no closed-form analytic solution, a numerical
solver has to be developed for analysing such system.

@@

@@

@@

Without loss of generality, 
we assume that $\cV = -\log\gamma$, thus $\zeta = -\log\gamma-\varPhi$:
\begin{eqnarray}
\varPhi + \log C &=& 0.
\end{eqnarray}

@@

\subsubsection{Highly charged particle}
\begin{eqnarray}
 \deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0, \\
 \deriv{C}{r} - \mbox{Du} \Laplacian_s (\varPhi - \log C) &=& 0.
\end{eqnarray}

>>>>

Recently, it has been conceived that such type of dynamics
can be very useful in transporting and manipulating micro-
and nanoscale objects for many nanotechnology applications
\cite{howse2007self,paxton2004catalytic,pumera2010electrochemically, nischang2007, leinweber2004}.
However, since the analytic model for these electrokinetic
phenomena has no closed-form analytic solution, a numerical
solver has to be developed for analysing such system.

@@

The dimensional boundary condition for $\mathbf{D}^* = \eps^*\mathbf{E}^*$ for a charged surface
with surface charge density $\sigma^*$ is
\begin{eqnarray}
\bn \cdot \pars{\eps^*\mathbf{E}^* - \eps^*_s\mathbf{E}^*_s} &=& \sigma^*,
\end{eqnarray}
and after nondimensionalization by 
normalizing the surface charge using $\sigma^* = \eps^* \varphi^* / a^* \delta$
and $\gamma = \eps^*_s / \eps^*$, yields:
\begin{eqnarray}
-\deriv{\varphi}{n} + \gamma \deriv{\varphi_s}{n} &=& \delta^{-1} \sigma.
\end{eqnarray}

@@

\subsubsection{Highly charged particle}
Following the derivation at \cite{schnitzer2012surface}, the boundary conditions at a spherical 
particle with high surface charge, $\sigma = \delta^{-1} \text{Bi}$ 
(where $\text{Bi} = O(1)$ is the Bikerman number):
\begin{eqnarray}
 \deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0, \\
 \deriv{C}{r} - \mbox{Du} \Laplacian_s (\varPhi - \log C) &=& 0, \\
 \bV &=& 4 \log 2 \bnabla_\mathcal{S} + \zeta \bnabla_\mathcal{S} \pars{\varPhi -\log C}, \\
 \zeta &=& \bar{\zeta} - \log C , \\
 \bar\zeta &=& 2 \log \sigma.
\end{eqnarray}

@@

Without loss of generality, 
we assume that $\cV = -\log\gamma$, thus $\zeta = -\log\gamma-\varPhi = \log (C/\gamma)$:
\begin{eqnarray}
\varPhi + \log C &=& 0.
\end{eqnarray}

@@

The slip velocity derivation is the same as for the inert particle:
\begin{eqnarray}
\bV &=& 
\zeta \cdot \bnabla_\mathcal{S} \varPhi 
+ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C. \\
\end{eqnarray}

### 2012-09-08 notes/work/ch02.tex
Add more figures
Review.
LaTeX

\subsubsection{Operator Representation}
System variable $\bx$ is defined as the concatenation $[\,\varPhi, C, V_r, V_\theta, P\,]$,
taking only values in the interior of the problem domain grid.
Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
\begin{eqnarray}
X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
\end{eqnarray}

The extended variables $\tilde X$ (including ``ghost'' point values) 
are computed by applying the following nonlinear operators:
\begin{eqnarray}
\tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta), \\
\tilde{C} &=& \cB_C(C, \varPhi), \\
\tilde{V_r} &=& \cB_{V_r}(V_r; \cU), \\
\tilde{V_\theta} &=& \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma), \\
\tilde{P} &=& P.
\end{eqnarray}
The extended system variable can be written as $\tilde{\bx} = \cB(\bx)$, 
where $\cB$ is the ``ghost'' point extension operator (derived using boundary conditions)
so the concatenated equations of the system (as described above) can be written 
as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable 
$\tilde{\bx}$, where $\cE$ is the conservation equations operator 
(derived by concatenation of the system equations).

The problem can be cast as the following non-linear system:
\begin{eqnarray}
\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx)
\end{eqnarray}
 where $\cO = \cE \circ \cB$.

@@

$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature method:
\begin{eqnarray}
F_\imath &=& \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i
\end{eqnarray}

>>>>

\subsubsection{Operator Representation}
System variable $\bx$ is defined as the concatenation $[\,\varPhi, C, V_r, V_\theta, P\,]$,
taking values in the interior of the problem domain grid and on the ``ghost'' points.
Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
\begin{eqnarray}
X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
\end{eqnarray}

The concatenated equations of the system (as described above) can be written 
as a non-linear operator $\cO(\bx) = \bzero$ acting on the system variable 
$\bx$, where $\cO$ is the concatenation of system equations operator 
(derived by concatenation of the system equations) together with
boundary conditions equations operators.

@@

$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule:
\begin{eqnarray}
F_\imath &=& \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i
\end{eqnarray}
